Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-07-08 paper/re-pro-badge.tex
automatically reproduce paper

This document, along with all included plots and tables, was generated from commit \href{https://github.com/FMatti/Rand-TRACE/tree/5832e99}{5832e99} at \url{https://github.com/FMatti/Rand-TRACE} on 2024-07-08 at 05:53:37 UTC.

>>>>

This document, along with all included plots and tables, was generated from commit \href{https://github.com/FMatti/Rand-TRACE/tree/a000fde}{a000fde} at \url{https://github.com/FMatti/Rand-TRACE} on 2024-07-08 at 06:45:20 UTC.
